A Longitudinal Analysis of the Privacy Paradox

### 2020-04-23 analyses_additional.Rmd
created new file "analyses additional"

# export bib library
r_refs("../bibliography/r-references.bib")
```

```{r datawrangling, include=F}
# first run "data_wranling.R", in order to create these objects
d_wide <- read_csv("../data/data_wide.csv")
d_wide_all <- read_csv("../data/data_wide_all.csv")
d_long <- read_csv("../data/data_long.csv")
```

```{r include=F}
# Extract descriptives to report in paper
desc <- d_wide %>% 
  summarize_at(vars(ends_with("_m")), funs(mean(., na.rm = TRUE), sd(., na.rm = TRUE)))
```

# Items
## Privacy Concern

The following deals with things that can happen on the Internet.

1. In general, how concerned are you about your privacy while using the Internet?
2. Are you concerned about online organizations not being who they claim they are?
3. Are you concerned about online identity theft?
4. Are you concerned about people you do not know obtaining personal information about you from your online activities?
5. Are you concerned that if you use your credit card to buy something on the Internet your credit card number will be obtained/intercepted by someone else?
6. Are you concerned that an email you sent may be read by someone else besides the person you sent it to?
7. Are you concerned that institutions or secret services could collect and analyze the data that you are disclosing on the Internet?
8. Are you concerned that website providers are tracking your online activities?
9. Are you concerned that you don’t know what other organizations or website providers are doing with you data?

(NA = "no Internet user / no reply", 1 = "Not concerned at all" : 5 = "very concerned")

## Attitude Toward Online Sharing of Personal Information

Now we will deal with information sharing on the Internet. Do you think that it is sensible to disclose the following pieces of information online, i.e., via the Internet?

1. Financial information (bank data, account balances…)
2. Medical information (health, medical records…)
3. Second name
4. First name
5. Residence
6. Street and house number
7. Email address
8. Phone number
9. Photos (of you)
10. Job (past and present)
11. Education

(NA = “no Internet user / no reply”, 1 = "not sensible at all", 2 = "somewhat not sensible", 3 = "in part", 4 = "somewhat sensible", 5 = "very sensible")

## Online Sharing of Personal Information

In the following, please indicate how often you disclose the following information on the Internet. How often do you disclose the following pieces of information online, i.e., on the Internet?

1. Financial information (bank data, account balances…)
2. Medical information (health, medical records…)
3. Second name
4. First name
5. Residence
6. Street and house number
7. Email address
8. Phone number
9. Photos (of you)
10. Job (past and present)
11. Education

(NA = “no Internet user / no reply”, 1 = "every day", 2 = "weekly", 3 = "monthly", 4 = "less than that", 5 = "never")

# Power Analyses

```{r power}
n_complete <- nrow(d_wide)
alpha <- .05
power <- .95
sesoi <- .1
n <- n_complete
n_apriori <- pwr.r.test(r = sesoi, sig.level = alpha, power = power)$n
power_achieved_h <- pwr.r.test(r = sesoi, sig.level = alpha, n = n, alternative = "greater")$power
alpha_balanced_h <- balance_errors(sesoi, n, one_tailed = TRUE)
power_balanced_h <- 1 - alpha_balanced_h
power_achieved_rq <- pwr.r.test(r = sesoi, sig.level = alpha, n = n)$power
alpha_balanced_rq <- balance_errors(sesoi, n, one_tailed = FALSE)
power_balanced_rq <- 1 - alpha_balanced_rq
```

A-priori power analyses revealed that N = `r n_apriori` people would be needed to find effects with a size of _r_ = `r sesoi` with a power of `r power`.

Overall, the data of `r n` respondents could be used for our analyses. As a result, alpha and beta errors were balanced when using an alpha of `r alpha_balanced_h %>% round(3)`, resulting in an achieved power of `r power_balanced_h %>% round(3)`.

# Sociodemographics

```{r}
age_m <- mean(d_wide$age)
age_sd <- sd(d_wide$age)
male_per <- mean(d_wide$male)
edu_col_per <- nrow(d_wide[d_wide$edu_num > 5, ]) / n_complete * 100
```

# Analysis of Missing Values

```{r cache=F}
d_tmp <- select(d_wide, -contains("_m"), -contains("tim"), -contains("T4"), -contains("T5"), -contains("per"), -contains("use"), -c(id, age, edu, edu_num, male))
test_mar <- TestMCARNormality(d_tmp)

# print patterns
as.data.frame(test_mar$patused)

# non-parametric test
(test_mar_p <- test_mar$pnormality)

# calculate percentage of missing data
na_per <- mean(c(d_wide$t1_na_per, d_wide$t2_na_per, d_wide$t3_na_per)) * 100
```

Visual inspection of the missing value patterns as well as the non-parametric test suggested that all missing values could be considered to be missing at random (_p_ `r test_mar$pnormality %>% td::my_round("p_txt")`).

# Factor Analyses
## Concerns about online privacy
### EFA

@@

## All Measures in one Model 
### Second Order

@@

### Extract Factor Scores

```{r}
d_fs <- lavPredict(get(paste("fit", name, no, sep = "_")), type = "ov") %>% 
  as.data.frame() %>% 
  mutate(t1_pri_con_fs = rowMeans(select(., starts_with("t1_pri"))),
         t2_pri_con_fs = rowMeans(select(., starts_with("t2_pri"))),
         t3_pri_con_fs = rowMeans(select(., starts_with("t3_pri"))),
         t1_inf_sha_att_fs = rowMeans(select(., starts_with("t1_inf_sha_att"))),
         t2_inf_sha_att_fs = rowMeans(select(., starts_with("t2_inf_sha_att"))),
         t3_inf_sha_att_fs = rowMeans(select(., starts_with("t3_inf_sha_att"))),
         t1_inf_sha_beh_fs = rowMeans(select(., starts_with("t1_inf_sha_beh"))),
         t2_inf_sha_beh_fs = rowMeans(select(., starts_with("t2_inf_sha_beh"))),
         t3_inf_sha_beh_fs = rowMeans(select(., starts_with("t3_inf_sha_beh")))
         ) %>% 
  select(contains("_fs"))
d_wide <- cbind(d_fs, d_wide)
```

# Correlation matrix and distributions

```{r Corrplot, fig.height = 8, fig.width = 8, size=5}
colnames(d_fs) <- c("Concerns\nT1", "Concerns\nT2" , "Concerns\nT3",
                    "Pos. Attitude\nT1", "Pos. Attitude\nT2" , "Pos. Attitude\nT3",
                    "Inf. Sharing\nT1", "Inf. Sharing\nT2" , "Inf. Sharing\nT3")

corr_plot <- ggpairs(d_fs,
                     # upper = list(continuous = wrap(td::cor_matrix, data = d_fs)),
                     lower = list(continuous = wrap(td::scat_plot, coords = c(1, 5, 1, 5)))) + 
  theme_bw()
print(corr_plot)
```

# ICCs

Next, we determine the Intraclass Correlation Coefficients (ICC), to determine how much variance in the measures is due to between-person differences versus within-person changes.

```{r}
fit <- lmer(pri_con_m ~ 1 + (1 | id), filter(d_long, wave < 4))
summary(fit)
(icc_pri_con <- icc(fit))

fit <- lmer(inf_sha_att_m ~ 1 + (1 | id), filter(d_long, wave < 4))
summary(fit)
(icc_inf_sha_att <- icc(fit))

fit <- lmer(inf_sha_beh_m ~ 1 + (1 | id), filter(d_long, wave < 4))
summary(fit)
(icc_inf_sha_beh <- icc(fit))
```

@@

In what follows, please find all information about our final model we present in the paper.

## Visualization

```{r, fig.cap="Visual representation of the estimated random-intercept cross-lagged panel model (RI-CLPM)."}
knitr::include_graphics("../figures/model_7.png")
```

## Results

# control variables
t1_pri_con_fs ~ age + edu_num + male
t2_pri_con_fs ~ age + edu_num + male
t3_pri_con_fs ~ age + edu_num + male
t1_inf_sha_beh_fs ~ age + edu_num + male
t2_inf_sha_beh_fs ~ age + edu_num + male
t3_inf_sha_beh_fs ~ age + edu_num + male
t1_inf_sha_att_fs ~ age + edu_num + male
t2_inf_sha_att_fs ~ age + edu_num + male
t3_inf_sha_att_fs ~ age + edu_num + male
'
fit <- sem(model, data = d_wide, orthogonal = TRUE, missing = "ML")
summary(fit, standardized = TRUE, fit.measures = TRUE, ci = TRUE)
```

# Additional Analyses
## RI-CLPM
### Assumptions
#### Multivariate Normal Distribution

```{r multivardis}
mult_norm_test <- mvn(d_fs)
print(mult_norm_test)
```

Results show that the assumption of multivariate normal distribution was violated. Hence, it'd be preferrable to conduct robust Maximum Likelihood Estimation. However, using robust estimation it's not possible to run SEM on all data using Full Information Maximum Likehoood (FIML). Given that we consider it more important to include as much information as possible and that estimators often produce similar results, we decided to estimate the following models using regular maximum likehood.

### Two Variables

Here, we look at the bivariate relations of privacy concerns and information sharing. This is interesting, because in the paper we also address privacy attitudes, thereby potentially attentuating the effect of privacy concerns. However, when analyzing only these two variables we do not find larger effects sizes.

@@

```{r cache=F}
save.image("../data/workspace.RData")
```

>>>>

load("data/workspace.RData") 
```
In what follows, we report the results of additional analyses that were also calculated. For example, for each measure we also report exploratory factor analyses, first order model solutions, and unconstrained solutions to estimate longitudinal  invariance.

# Measures
## Concerns about online privacy
### EFA

@@

## Baseline Model
### Second Order

@@

@@

In what follows, we report additional models, which are also related to our research question.

## RI-CLPM
### Two Variables

Here, we look at the bivariate relations of privacy concerns and information sharing. This is interesting, because in the paper we also address privacy attitudes, thereby potentially attenuating the effect of privacy concerns. However, when analyzing only these two variables we do not find larger effects sizes.

@@
